### 2020-08-13 5_evaluation.tex
Push new paragraph for scalability.

PaRSEC, StarPU and Regent
rely on runtime analysis that can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially by allowing the user to omit tasks not directly
dependent on those executed by a given node. However, this approach still requires checks that scale with
node count and thus limit scalability~\cite{PARSEC_DTD}. Compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG improves over DTD 
by performing DAG expansion at compile time~\cite{PARSEC_DTD}, but
retains dynamic checks that limit scalability. PaRSEC shard includes additional manual optimizations over DTD, completely eliminating these dynamic checks. Regent
uses a compile-time optimization to improve
scalability~\cite{ControlReplication17}; the increase in METG beyond 16 nodes is due to a known bug in Realm barrier migration which the Realm Task Bench implementation is able to manually work around.

>>>>

PaRSEC, StarPU and Regent rely on runtime analysis that can suffer
from scalability bottlenecks if every node must consider the tasks
executing on all other nodes. Although all three systems offer ways to
improve scalability, these methods are not equally effective. PaRSEC
DTD and StarPU allow users to manually prune tasks to reduce overhead;
however the checks are not reduced to zero. Similarly, PaRSEC PTG uses
compile-time optimizations to avoid the need for manual pruning, but
still targets the PaRSEC DTD runtime and thus incurs some
overhead. Figure~\ref{fig:metg-compute} shows that these models do not
provide ideal scalability, as seen by METG values that rise with
increasing node count. Regent uses a compile-time optimization to
generate code with a constant overhead per
node~\cite{ControlReplication17}. Of the three systems, Regent is the
only one that achieves ideal scalability while preserving its
original, implicitly parallel programming model. The others can
achieve ideal scalability but require increasing levels of manual
intervention. PaRSEC \lstinline{shard} includes additional manual
optimizations over DTD to completely eliminate dynamic checks. StarPU
\lstinline{expl} is written in an explicitly parallel style using MPI
for communication, and thus avoids any analysis bottleneck. These
results indicate that the underlying systems are capable of scalable
execution, but that the dynamic checks incurred by the implicitly
parallel programming models hinder that scalability.
